---
title: Evaluation Randomisiert-Kontrollierter Studien und Experimente mit \textsf{R}
subtitle: Aufbau & Hintergrund
author: Prof. Dr. David Ebert & Mathias Harrer
date: Graduiertenseminar TUM-FGZ
institute: Psychology & Digital Mental Health Care, Technische Universität München
output: binb::metropolis
fontsize: 11pt
bibliography: bib.bib
csl: apa.csl
monofont: "Fira Code"
mainfont: "Fira Sans"
header-includes: |
  ```{=latex}
  \makeatletter
  \let\@@magyar@captionfix\relax
  \makeatother
  \usepackage{xcolor}
  \definecolor{protectBlue}{RGB}{48,124,148}
  \definecolor{protectGreen}{RGB}{161, 198, 66}
  \definecolor{verywhite}{rgb}{1, 1, 1}
  \usepackage{multicol}
  \hypersetup{colorlinks,citecolor=protectGreen,
    filecolor=red,linkcolor=protectGreen,urlcolor=blue}
  \setbeamercolor{progress bar}{fg=protectGreen}
  \setbeamercolor{alerted text}{fg=protectGreen}
  \setbeamercolor{frametitle}{bg=protectBlue}
  \setbeamercolor{normal text}{fg=protectBlue}
  \titlegraphic{%
  \hspace*{6cm}~%
  \includegraphics[width=2cm]{logo/tum-lightblue}
  \hspace*{0.3cm}~%
  \includegraphics[width=2cm]{logo/protect}}
  \setbeamertemplate{frame footer}{Evaluation Randomisiert-Kontrollierter Studien und Experimente mit \textsf{R}}%         <- !!SET FOOTER TITLE!!
  \makeatletter
  \setlength{\metropolis@frametitle@padding}{2.2ex}
  \setbeamertemplate{footline}{%
      \begin{beamercolorbox}[wd=\textwidth, sep=0.7ex]{footline}
          \usebeamerfont{page number in head/foot}%
          \usebeamertemplate*{frame footer}
          \hfill%
          \usebeamertemplate*{frame numbering}
      \end{beamercolorbox}%
  }
  \setbeamertemplate{frametitle}{%
    \nointerlineskip%
    \begin{beamercolorbox}[%
        wd=\paperwidth,%
        sep=0pt,%
        leftskip=\metropolis@frametitle@padding,%
        rightskip=\metropolis@frametitle@padding,%
      ]{frametitle}%
    \metropolis@frametitlestrut@start%
    \insertframetitle%
    \nolinebreak%
    \metropolis@frametitlestrut@end%
    \hfill
    \includegraphics[height=2ex,keepaspectratio]{logo/tum_white}
    \end{beamercolorbox}%
  }
  \newlength{\cslhangindent}
  \setlength{\cslhangindent}{1.5em}
  \newenvironment{CSLReferences}[3]%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  ```
---

```{r,setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

# First Section

## First Frame

Hello, world!

# Second Section

## Second Frame

### Bulleted Lists
- Element A
- Element B
    - B.1
    - B.2
- Element C    

# Elements

## Typography

```
The theme provides sensible defaults to
\emph{emphasize} text, \alert{accent} parts
or show \textbf{bold} results.

In Markdown, you can also use _emphasize_ and **bold**.
```

\begin{center}becomes\end{center}

The theme provides sensible defaults to \emph{emphasize} text,
\alert{accent} parts or show \textbf{bold} results [@arendt1989leben; @smit2006costs; @andersson2009internet].

In Markdown, you can also use _emphasize_ and **bold**.


## Math

\begin{equation*}
    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
\end{equation*}


## R Figure Example

The following code generates the plot on the next slide (taken from
`help(bxp)` and modified slightly):

```{r pressureCode, eval=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```  


## R Figure Example
  
```{r pressureFig, echo=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```  

## R Table Example
  
A simple `knitr::kable` example:  

```{r kableEx}
knitr::kable(mtcars[1:5, 1:8],
             caption="(Parts of) the mtcars dataset")
```

## Resources

### For more information:
- See the [Metropolis repository](https://github.com/matze/mtheme) for more on Metropolis
- See the [RMarkdown repository](https://github.com/rstudio/rmarkdown) for more on RMarkdown
- See the [binb repository](https://github.com/eddelbuettel/binb) for more on binb 
- See the [binb vignettes](https://github.com/eddelbuettel/binb/vignettes) for more examples.

## References {.allowframebreaks}






